A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828: supplementary material

### 2018-09-11 inst/examples/201808-HistoricalMethods-Supplement.Rmd
ok

  complete <- round(100 * colMeans(!is.na(dd)), 1)
  unique <- apply(dd, 2, function (x) {length(unique(x))})

@@

# Add Footnote
w[which(w$Field == "Topic"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Topic"), "SNB (%)"]), "*")
w[which(w$Field == "Publisher"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Publisher"), "SNB (%)"]), "*")

kable <- knitr::kable
knitr::kable(w, format = "markdown")

>>>>

  complete <- round(100 * colMeans(!is.na(dd)), 1)

  # complete <- gsub("^100$", "100.0", complete)
  # complete <- 100 * colMeans(!is.na(dd))
  unique <- apply(dd, 2, function (x) {length(unique(x))})

@@

# Add Footnote
w[,2] <- as.character(w[,2])
w[,3] <- as.character(w[,3])
w[which(w$Field == "Topic"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Topic"), "SNB (%)"]), "*")
w[which(w$Field == "Publisher"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Publisher"), "SNB (%)"]), "*")
w[,3] <- gsub("100", "100.0", w[,3])
w[,3] <- gsub("^94$", "94.0", w[,3])
w[,2] <- gsub("100", "100.0", w[,2])
w[,2] <- gsub("^98$", "98.0", w[,2])
w[,2] <- gsub("^93$", "98.0", w[,2])
kable <- knitr::kable
knitr::kable(w, format = "markdown", digits = 1)
